???

### 2017-01-24 docs/language_constraint.tex

\begin{table}[!t]
\small
\begin{tabular}{|p{.95cm}|p{6cm}|} \hline
{\bf Type} & {\bf Example} \\ \hline
{\it Original} story & My mother loves clocks that chime.	Her house is full of them.	She sets them each a little different so she can hear them chime.	It sounds like a bell tower during a wedding in her house all day.	{\color{blue}{When I visit I stop them or I'd never be able to sleep at night.}} \\ \hline
{\it Correct} story & Kathy went shopping.	She found a pair of great shoes.	The shoes were \$300.	She bought the shoes.	{\color{green}{She felt buyer's remorse after the purchase.}} \\ \hline
{\it Wrong} story & I Kathy went shopping.	She found a pair of great shoes.	The shoes were \$300.	She bought the shoes.	Kathy hated buying shoes.	{\color{red}{Kathy hated buying shoes.}} \\ \hline
\end{tabular}
\caption{\label{ROC-example}}
Examples of stories from the story cloze task. The first row shows an original story written by one author. 
The second and third row show two endings of the same story: a {\it correct} ending and a {\it wrong} one.
%\end{center}
\end{table}

@@

\isection{The Cloze Story Task}{ROC_Story}\roy{We should start with a general paragraph reminding the reader of the problem and why we are using this corpus.}
Developed as an effort to simplify\roy{``simplify'' is not the right term here. {\it Facilitate} maybe? }  the representation and learning of commonsense knowledge, the \textit{Cloze Story Task} \cite{Mostafazadeh:2016} has become the Shared Task for the LSDSem workshop.\roy{Not sure that this sentence is so terrible, but I would not put the focus on the shared task. This is a rather minor detail and has very little relevance to our story. Think about what we want to reader who has very little time or energy to know. 
Specifically, I would start with few very general details and motivation (as you did), but then directly move to mention the interesting design decisions they took, 
which actually raise  very different type of research questions, which we tackle in this paper. Then you can move to describe it more formally, as you do below (you can mention the shared task there if you want, not sure it's even necessary).} % this is a terrible sentence.
The task provides two types of datasets: the \textit{ROC Stories} and the \textit{Story Cloze test sets}.

\paragraph{ROC Stories}
consist of $98,163$ five-sentence commonsense stories, collected on AMT\roy{I would use ``Amazon Mechanical Turk (AMT)'' here, and AMT from now on}. Workers were instructed to write a coherent story where something happens, and with a clear beginning and end. To collect a broad spectrum of commonsense knowledge, there was no imposed subject for the stories.
\paragraph{Story Cloze} test sets were created on AMT, using a subset of ROC Stories. Presented with the first four sentences of a story, workers were asked to write a ``right'' and a ``wrong'' ending. \royb{The ending}{Both endings} had to complete the story using a character in it, and when read out of context, had to be ``realistic and sensible'' \cite{Mostafazadeh:2016}.

The resulting stories were then individually rated for coherence and meaningfulness by AMT workers. Only stories with a coherent and meaningful ``right'' ending and a neutral ``wrong'' ending were selected for the test, yielding $3,744$ test stories. \ms{Hope the ``neutral'' thing makes sense, I didn't know how else to explain 4.2.2 of the Story cloze paper.}\roy{Reading 4.2.2, it seems that they were not targeting badly phrased ``wrong'' sentences, but just the stories as a whole, and validated that all ``right'' stories were valid and all ``wrong'' stories were invalid (unless this is how you read the -1 option in their description, which is not addressed anywhere else in the text). If I am correct, I would write this and explicitly mention that no validation was performed on the ending level.}

\roy{The following might belong in the related work section, but probably more relevant here: I would add a section about performance on this task, stating that the authors tried quite a few baselines and showed that all pretty much fail on the task, and other than that there was just one paper that got slightly better results.
This is a place to make two more arguments: 
(a) the low results obtained by the various baseline methods, as well as the low number of works (only one) that improved results on this task, compared to other similar tasks published in recent years (SQUAD, SNLI, CNN/Daily Mail., etc.), indicate that this is task is relatively hard, even for machine reading systems that has made a huge progress in recent years. 
(b) To the best of our knowledge, this is the first work to consider the style differences between the two endings, rather than the setup suggested by the author. \\
Btw, this could be a good place to mention the shared task.}

@@

\begin{itemize}
\item{Length} The number of words in the sentence.
\item{Word n-grams} We use sequences of 1-5 words. Following \cite{Tsur:2010,Schwartz:2013}, we distinguish between high frequency and low frequency words. 
Specifically, we replace content words with their part-of-speech tags (Nouns, Verbs, Adjectives and Adverbs).
\item{Character n-grams} Character n-grams are one of the most useful features in identifying author style \cite{Stamatatos:2009}. 
We used character 5-grams.
\end{itemize}

@@

\begin{table}[!t]
\begin{center}
\small
\begin{tabular}{|c|c|} \hline
{\bf Model} & {\bf Results} \\ \hline
{DSSM} \cite{Mostafazadeh:2016} & 0.585 \\ \hline
{ LexVec} \cite{Salle:2016} & 0.599 \\ \hline
{RNN}		& 0.677 \\ \hline
{\bf Our Model} & {\bf 0.715} \\ \hline
{\bf Combined (Our model, RNN)} & {\bf 0.751} \\ \hline\hline
{ tbmihaylov (shared task)} & 0.711\\ \hline
{ Niko (shared task)}	& 0.7\\ \hline\hline
Human judgment & 1 \\ \hline
\end{tabular}
\end{center}
\caption{\label{cloze_results}}
Results on the test set of the cloze story task. 
Upper part are published results (Lexvec results are taken from \cite{Speer:2016}).
Bottom part are taken from the cloze task shared task webpage.
\end{table}

@@

\paragraph{Neural Language Model.}
\ms{Below is a messy dump of all the hyper parameters... Didn't know how many details were needed}\roy{The level of description seems fine (we might remove some of them if space is an issue, but for now it's good. What I'm missing here are (a) an introductory 1-2  sentences to what are we doing here (I realize that it is not 100\% clear from the intro what is the role of these experiments other than showing that we have STOA results, so this can come later\\
(b) A one-sentence description of your model. Currently, there is no clear separation between the model (RNN using LSTM) and the technical details. 
Some general description of the model, and specifically the motivation behind (nothing fancy, just saying that we applied state-of-the-art LM tools, 
which resemble the tools the authors had in mind when they designed the task).}

We trained a simple RNN Language model \cite{mikolov2010recurrent} using a single-layer LSTM \cite{hochreiter1997long} of hidden dimension $h=512$.
We used the ROC Stories for training, setting aside $10\%$ for validation of the language model. We replaced all words occuring less than 3 times by a special out-of-vocabulary character, yielding a vocabulary size of $|V|=21,582$.
Only during training, we applied a dropout rate of 60\% while running the LSTM over all 5 sentences of the stories. Using AdamOptimizer \cite{kingma2014adam} and a learning rate of $\eta=.001$, we trained with backpropagation on cross-entropy. % minibatches of $50$ stories.
% h=512, dropout rate of 60%, V=21582, 10% validation set

To construct features for the Story Cloze task, we scored each of the two endings using our neural language model. We computed the probability of each ending given the first four sentences $p_\theta(ending|story)$, as well as the probability of the endings out of context $p_\theta(ending)$. We also included the likelihood ratio $\frac{p_\theta(ending|story)}{p_\theta(ending)}$ into our classifier.\roy{This will probably change once we have the rest of the paper, but generally a few things that are missing:
(a) performance of the model as a standalone (both how we evaluated it and how much it got).
(b) modifying this paragraph to indicate that in order to combine between the style features presented in this paper and this model, we did the above.
(c) results of the combination (75.1\%).\\
These numbers might best fit in a small table.}

>>>>

\begin{table}[!t]
\small
\begin{tabular}{|p{.95cm}|p{6cm}|} \hline
{\bf Type} & {\bf Example} \\ \hline
{\it Original} story & My mother loves clocks that chime.	Her house is full of them.	She sets them each a little different so she can hear them chime.	It sounds like a bell tower during a wedding in her house all day.	{\color{blue}{When I visit I stop them or I'd never be able to sleep at night.}} \\ \hline
{\it Correct} story & Kathy went shopping.	She found a pair of great shoes.	The shoes were \$300.	She bought the shoes.	{\color{green}{She felt buyer's remorse after the purchase.}} \\ \hline
{\it Wrong} story & Kathy went shopping.	She found a pair of great shoes.	The shoes were \$300.	She bought the shoes.	{\color{red}{Kathy hated buying shoes.}} \\ \hline
\end{tabular}
\caption{\label{ROC-example}}
Examples of stories from the story cloze task. The first row shows an original story written by one author. 
The second and third row show two endings of the same story: a {\it correct} ending and a {\it wrong} one.
%\end{center}
\end{table}

@@

\isection{The Cloze Story Task}{ROC_Story}
Writing tasks are plentiful on Amazon Mechanical Turk (AMT) \ms{cite various examples?}. As a testbed for our analyses, we chose the \textit{Story Cloze Task} \cite{Mostafazadeh:2016}, during which workers were asked to write intuitive and counter-intuitive endings to short stories. This task is particularly interesting in that the two endings were written by the same author, for the same story, allowing for careful comparison.

Originally, the task was developed as an effort to facilitate representation and learning of commonsense knowledge. For that purpose, the creators crowdsourced the creation of two types of datasets: the \textit{ROC Stories} and the \textit{Story Cloze test sets}.
%\roy{Not sure that this sentence is so terrible, but I would not put the focus on the shared task. This is a rather minor detail and has very little relevance to our story. Think about what we want to reader who has very little time or energy to know. Specifically, I would start with few very general details and motivation (as you did), but then directly move to mention the interesting design decisions they took, which actually raise  very different type of research questions, which we tackle in this paper. Then you can move to describe it more formally, as you do below (you can mention the shared task there if you want, not sure it's even necessary).} % this is a terrible sentence.

\paragraph{ROC Stories}
consist of $98,163$ five-sentence commonsense stories, collected on AMT. Workers were instructed to write a coherent story where something happens, and with a clear beginning and end. To collect a broad spectrum of commonsense knowledge, there was no imposed subject for the stories.
\paragraph{Story Cloze} test sets were created on AMT, using a subset of ROC Stories. Presented with the first four sentences of a story, workers were asked to write a ``right'' and a ``wrong'' ending. Both endings had to complete the story using a character in it, and when read out of context, had to be ``realistic and sensible'' \cite{Mostafazadeh:2016}.

The resulting stories, matched with each ending, were then individually rated for coherence and meaningfulness by AMT workers. Only stories rated as simultaneaously coherent with ``right'' ending and neutral with a ``wrong'' ending were selected for the test, yielding $3,744$ test stories. It is worth noting that workers rated the stories as a whole, not the endings; no selection was done on the endings alone.
%\ms{Hope the ``neutral'' thing makes sense, I didn't know how else to explain 4.2.2 of the Story cloze paper.}\roy{Reading 4.2.2, it seems that they were not targeting badly phrased ``wrong'' sentences, but just the stories as a whole, and validated that all ``right'' stories were valid and all ``wrong'' stories were invalid (unless this is how you read the -1 option in their description, which is not addressed anywhere else in the text). If I am correct, I would write this and explicitly mention that no validation was performed on the ending level.}

\paragraph{Benchmarks}
~\ms{Like you said, maybe this belongs in related work, but for now I'll put it here}
The creators of the dataset implemented various benchmarks, using surface level features as well as narrative informed ones. Compared to similar tasks \cite{CNN, SQUAD, SNLI}, the baselines perform relatively poorly, indicating that the task is a relatively hard one. 
%\roy{The following might belong in the related work section, but probably more relevant here: I would add a section about performance on this task, stating that the authors tried quite a few baselines and showed that all pretty much fail on the task, and other than that there was just one paper that got slightly better results. This is a place to make two more arguments:  (a) the low results obtained by the various baseline methods, as well as the low number of works (only one) that improved results on this task, compared to other similar tasks published in recent years (SQUAD, SNLI, CNN/Daily Mail., etc.), indicate that this is task is relatively hard, even for machine reading systems that has made a huge progress in recent years. (b) To the best of our knowledge, this is the first work to consider the style differences between the two endings, rather than the setup suggested by the author. \\ Btw, this could be a good place to mention the shared task.}

@@

\begin{itemize}
\item\textit{\textbf{Length~}} The number of words in the sentence.
\item\textit{\textbf{Word n-grams~}} We use sequences of 1-5 words. Following \cite{Tsur:2010,Schwartz:2013}, we distinguish between high frequency and low frequency words. 
Specifically, we replace content words with their part-of-speech tags (Nouns, Verbs, Adjectives and Adverbs).
\item\textit{\textbf{Character n-grams~}} Character n-grams are one of the most useful features in identifying author style \cite{Stamatatos:2009}. 
We used character 5-grams.
\end{itemize}

@@

\begin{table}[!t]
\begin{center}
\small
\begin{tabular}{|c|c|} \hline
{\bf Model} & {\bf Results} \\ \hline
{DSSM} \cite{Mostafazadeh:2016} & 0.585 \\ \hline
{ LexVec} \cite{Salle:2016} & 0.599 \\ \hline
{RNN}		& 0.681 \\ \hline
{\bf Our Model} & {\bf 0.715} \\ \hline
{\bf Combined (Our model, RNN)} & {\bf 0.751} \\ \hline\hline
{ tbmihaylov (shared task)} & 0.711\\ \hline
{ Niko (shared task)}	& 0.7\\ \hline\hline
Human judgment & 1 \\ \hline
\end{tabular}
\end{center}
\caption{\label{cloze_results}}
Results on the test set of the cloze story task. 
Upper part are published results (Lexvec results are taken from \cite{Speer:2016}).
Bottom part are taken from the cloze task shared task webpage.
\end{table}

@@

\paragraph{Neural Language Model.}
~\ms{This needs to be placed somewhere else LOL}
~\ms{Below is a messy dump of all the hyper parameters... Didn't know how many details were needed}
\roy{The level of description seems fine (we might remove some of them if space is an issue, but for now it's good. What I'm missing here are (a) an introductory 1-2  sentences to what are we doing here (I realize that it is not 100\% clear from the intro what is the role of these experiments other than showing that we have STOA results, so this can come later\\
(b) A one-sentence description of your model. Currently, there is no clear separation between the model (RNN using LSTM) and the technical details. 
Some general description of the model, and specifically the motivation behind (nothing fancy, just saying that we applied state-of-the-art LM tools, 
which resemble the tools the authors had in mind when they designed the task).}

To leverage the genre of these short stories, we train a recurrent language model (RLM) \cite{mikolov2010recurrent}, which are used to achieve state-of-the-art performance on various tasks (e.g. machine translation). Training this RLM on the ROC stories, we harness the unsupervised, single-ended stories, which boosts performance on the Story Cloze task.

We trained an RLM using a single-layer LSTM \cite{hochreiter1997long} of hidden dimension $h=512$.
We used the ROC Stories for training, setting aside $10\%$ for validation of the language model. We replaced all words occuring less than 3 times by a special out-of-vocabulary character, yielding a vocabulary size of $|V|=21,582$.
Only during training, we applied a dropout rate of 60\% while running the LSTM over all 5 sentences of the stories. Using AdamOptimizer \cite{kingma2014adam} and a learning rate of $\eta=.001$, we trained with backpropagation on cross-entropy. % minibatches of $50$ stories.
% h=512, dropout rate of 60%, V=21582, 10% validation set

% Eval
On its own, our neural language model performs moderately on the Story Cloze test. As hinted at by the creators of this task, simple language models aren't enough to do well. In fact, using our neural LM and selecting endings based on $p_\theta(ending|story)$, we obtain only $55\%$ accuracy. When using the likelihood ratio $\frac{p_\theta(ending|story)}{p_\theta(ending)}$ to select endings, we obtain $68\%$. This doesn't beat reported SOTA, which is why we included these features into our stylistic driven model.

% To construct features for the Story Cloze task, we scored each of the two endings using our neural language model. We computed the probability of each ending given the first four sentences $p_\theta(ending|story)$, as well as the probability of the endings out of context $p_\theta(ending)$. We also included the likelihood ratio $\frac{p_\theta(ending|story)}{p_\theta(ending)}$ into our classifier.
%\roy{This will probably change once we have the rest of the paper, but generally a few things that are missing:(a) performance of the model as a standalone (both how we evaluated it and how much it got). (b) modifying this paragraph to indicate that in order to combine between the style features presented in this paper and this model, we did the above.(c) results of the combination (75.1\%).\\These numbers might best fit in a small table.}
